### 2023-04-22 chapter2/chapter2.tex
Changed subsection title to use IDRs and not disorder regions

\subsection{Disorder regions have distinct patterns of residue substitution}
To gain insight into the substitution patterns of amino acid residues in disorder and order regions, we fit substitution models to meta-alignments sampled from the respective sets of filtered regions. These models are probabilistic descriptions of sequence evolution and are parameterized in terms of the one-way rates of change from one residue to another. Thus, the rates are not necessarily equal for a given pair of residues when the initial and target residues are swapped. For example, the rate of change of valine to tryptophan can be distinct from that of tryptophan to valine. In practice, substitution models are typically constrained to fulfill a condition called time-reversibility, as this converts a difficult multivariate optimization of the tree's branch lengths into a series of simpler univariate optimizations~\cite{Felsenstein1981}. A common method for fulfilling this condition is parameterizing the model in terms of a frequency vector, $\boldsymbol \pi$, and an exchangeability matrix, $S$. The frequency vector determines the model's expected residue frequencies at equilibrium, meaning the model dictates that all sequences eventually approach this distribution, no matter their initial composition. The exchangeability matrix is symmetric ($s_{ij} = s_{ji}$) and encodes the propensity for two residues to interconvert. Because the rate of change from residue $i$ to residue $j$ is given by $r_{ij} = s_{ij}\pi_{j}$, higher exchangeability coefficients yield higher rates of conversion. Thus, exchangeability coefficients are frequently interpreted as a measure of biochemical similarity between residues.

>>>>

\subsection{IDRs have distinct patterns of residue substitution}
To gain insight into the substitution patterns of amino acid residues in disorder and order regions, we fit substitution models to meta-alignments sampled from the respective sets of filtered regions. These models are probabilistic descriptions of sequence evolution and are parameterized in terms of the one-way rates of change from one residue to another. Thus, the rates are not necessarily equal for a given pair of residues when the initial and target residues are swapped. For example, the rate of change of valine to tryptophan can be distinct from that of tryptophan to valine. In practice, substitution models are typically constrained to fulfill a condition called time-reversibility, as this converts a difficult multivariate optimization of the tree's branch lengths into a series of simpler univariate optimizations~\cite{Felsenstein1981}. A common method for fulfilling this condition is parameterizing the model in terms of a frequency vector, $\boldsymbol \pi$, and an exchangeability matrix, $S$. The frequency vector determines the model's expected residue frequencies at equilibrium, meaning the model dictates that all sequences eventually approach this distribution, no matter their initial composition. The exchangeability matrix is symmetric ($s_{ij} = s_{ji}$) and encodes the propensity for two residues to interconvert. Because the rate of change from residue $i$ to residue $j$ is given by $r_{ij} = s_{ij}\pi_{j}$, higher exchangeability coefficients yield higher rates of conversion. Thus, exchangeability coefficients are frequently interpreted as a measure of biochemical similarity between residues.
